Type Refinements for the Working Class

### 2015-11-15 paper.tex
slight clarification of internal judgment

  It often happens that the evidence for a judgment is the knowledge of the
  meaning of a new form of judgment. This can be neatly expressed in our topos
  using the subobject classifier $\Omega$, where the evidence of $\Omega$ at
  $\Upsilon$ gives rise to an \emph{internal judgment} which is defined at all
  $\Upsilon'$ for which we have $\Of{\rho}{\Upsilon\inj\Upsilon'}$.  A
  \emph{global internal judgment} is a section
  $\Of{J}{\int_\Upsilon\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\Omega}}$, which can
  be externalized as a judgment $\Of{\Embed{J}}{\mathbb{J}}$ whose derivations
  at $\Upsilon$ are the arrows
  $\Of{\phi}{\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\mathbbold{1}}}$ such that the
  following diagram commutes:
  \[
    \begin{tikzcd}
      \IMode{\Yoneda{\Upsilon}}
        \arrow[r, dashed, "\OMode{\phi}"]
        \arrow[rd, "\IMode{J_\Upsilon}"']
      & \IMode{\mathbbold{1}} \arrow[d, "\IMode{\mathbf{true}}"] \\
      & \IMode{\Omega}
    \end{tikzcd}
  \]

>>>>

  It often happens that the evidence for a judgment is the knowledge of the
  meaning of a new form of judgment. This can be neatly expressed in our topos
  using the subobject classifier $\Omega$, where the evidence of $\Omega$ at
  $\Upsilon$ gives rise to an \emph{internal judgment} which is defined at all
  $\Upsilon'$ for which we have $\Of{\rho}{\Upsilon\inj\Upsilon'}$.

  A \emph{global internal judgment} is a section
  $\Of{J}{\int_\Upsilon{\Omega^{\mathbbold{1}}}(\Upsilon)}\cong
  \IMode{\int_\Upsilon\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\Omega}}$, which can
  be externalized as a judgment $\Of{\Embed{J}}{\mathbb{J}}$ whose derivations
  at $\Upsilon$ are the arrows
  $\Of{\phi}{\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\mathbbold{1}}}$ such that the
  following diagram commutes:

  \[
    \begin{tikzcd}
      \IMode{\Yoneda{\Upsilon}}
        \arrow[r, dashed, "\OMode{\phi}"]
        \arrow[rd, "\IMode{J_\Upsilon}"']
      & \IMode{\mathbbold{1}} \arrow[d, "\IMode{\mathbf{true}}"] \\
      & \IMode{\Omega}
    \end{tikzcd}
  \]
